---
title: "Creating a Mayo-Themed remark.js presentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a Mayo-Themed remark.js presentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css echo = FALSE}
.shadow {
  box-shadow: 0 .5rem 1rem rgba(0,0,0,.15) !important;
}
```

# Overview

`mayodown::mayomoon_reader` provides a convenient wrapper and styled template for `xaringan::moon_reader`.  See the resources below for more information:

- [GitHub Page](https://github.com/yihui/xaringan)

- [Documentation Slides](https://slides.yihui.org/xaringan)

# Basic Usage

The theme can be used by including it in the document YAML, as shown below.

```yaml
---
title: "A Title For Your Presentation"
author: "Author"
date: "2019-12-23 (updated: `r Sys.Date()`)"
output: mayodown::mayomoon_reader
subtitle: "Subtitle"
institute: "Mayo Clinic - HSR"
---
```

# Sample output

```{r echo=FALSE, include=FALSE}
rmarkdown::render("../inst/examples/moon_reader_example.Rmd", output_dir = "../docs/articles/")
```


<div class="embed-responsive embed-responsive-16by9 shadow">
<iframe  class="embed-responsive-item" align = "center" width = "100%" height = "600px" allow="fullscreen" src="moon_reader_example.html#zoom=133"/>
</div>

# Additional Arguments

`mayodown::mayohtml` is simply a wrapper around `xaringan::moon_reader()` and the same arguments can be used.  Some parameters have different default values set, however.
